\LARGE \bf When Children Teach a Robot to Write

### 2014-12-10 main.tex
Re-anonymized + new title proposal

\title{\LARGE \bf
Children Teach a Robot to Write: A Teachable Robotic Agent which Engages in Simulated Handwriting %still not sure
}

\numberofauthors{3} 
\author{
\alignauthor
Deanna Hood\\
Séverin Lemaignan\\
Pierre Dillenbourg\\
   \affaddr{Computer-Human Interaction in Learning and Instruction Laboratory (CHILI)}\\
   \affaddr{École Polytechnique Fédérale\\ de Lausanne (EPFL)}\\
   %\affaddr{CH-1015 Lausanne, Switzerland}\\
   \email{firstname.lastname@epfl.ch}
% \alignauthor
% Rafael Garcia\\
%    \affaddr{Computer Vision and Robotics Group (ViCOROB)}\\
%    \affaddr{University of Girona}\\
%    \affaddr{Girona, Spain}
}

@@

   \label{fig:naoWriting}
\end{figure}
\footnotetext{See \url{https://www.youtube.com/watch?v=2qWFSJRxCU0} for a video of the synchronised 
writing demonstration. }

@@

The source code for the teachable robotic handwriting partner has been made 
available at \url{https://github.com/chili-epfl/cowriter_letter_learning}.

>>>>

\title{\LARGE \bf
% what about:
When Children Teach a Robot to Write
% ?
}

\numberofauthors{1} 
%\author{
%\alignauthor
%Deanna Hood, Séverin Lemaignan, Pierre Dillenbourg\\
%   \affaddr{Computer-Human Interaction in Learning and Instruction Laboratory (CHILI)}\\
%   \affaddr{École Polytechnique Fédérale\\ de Lausanne (EPFL)}\\
%   %\affaddr{CH-1015 Lausanne, Switzerland}\\
%   \email{firstname.lastname@epfl.ch}
%}

@@

   \label{fig:naoWriting}
\end{figure}
%\footnotetext{See \url{https://www.youtube.com/watch?v=2qWFSJRxCU0} for a video of the synchronised 
\footnotetext{See \url{[anonymized]} for a video of the synchronised 
writing demonstration. }

@@

The source code for the teachable robotic handwriting partner has been made 
%available at \url{https://github.com/chili-epfl/cowriter_letter_learning}.
available at \url{[anonymized]}.
